Ecological validity of detecting data fabrication in experimental studies.

### 2016-04-25 submission/manuscript.Rmd
Redo the spreadsheets for study 1, update manuscript, add qualtrics questions

Thirty-six fabricated sets of summary results were also collected for all four anchoring studies. We sampled 2,038 American psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS). Psychology researchers were sampled to improve familiarity with the anchoring effect [@jacowitz1995], for which summary results were fabricated. U.S. researchers were sampled to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies. WoS was searched on October 13, 2015. In total, 2,038 unique corresponding e-mails were extracted from 2,014 papers (due to multiple corresponding authors).

The full sample frame was digitally approached to participate in this study on March XX, 2016 (invitation: osf.io/XXXX). The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-address saved at all). The researchers were fully informed that the study would require them to fabricate data and that we conducted this study to test the validity of statistical methods to detect data fabrication. Participants were also informed they could stop at any time without providing a reason. If they wanted, participants received a $30 Amazon gift card as compensation for their participation for which they had to provide their email address. These email addresses were unlinked from email addresses upon completion of the study and sending out the gift cards.

@@

To detect data fabrication in a set of summary results, we first apply the "variance of variances" method [@simonsohn2013] on the fabricated standard deviations across the four anchoring studies. This method tests whether the observed variances contain a reasonable amount of variation expected based on stochastic sampling processes. For example, if four independent samples all yield the variance of 2.22, this could be considered excessively consistent when the probability that this amount of consistency (or more), given genuine samples, is less than 1 out of 1000.

To compute the "variance of variances" method we use the following procedure. First, we compute the standardized variation in the observed variances for each of the four studies. 
Second, we compute the mean of these standardized variations, which results in one summary statistic that captures the variation in the variances across all four anchoring studies.
Third, in order

Second, we apply the reversed Fisher method to the fabricated nonsignificant *p*-values twice, one for the gender effects hypothesis and once for the interaction effects hypothesis, in order to detect data fabrication. The Fisher method [@fisher1925] tests for evidence of an effect in a set of *p*-values and has previously been used as a meta-analytic method [@hong2008], but we adjust it here to test for results that are overly consistent with the null hypothesis. The original Fisher method is computed as

$\chi^2_{2k}=-2\sum\ln(p_i)$

>>>>

Thirty-six fabricated sets of summary results were also collected for all four anchoring studies. We sampled 2,038 American psychology researchers who published a peer-reviewed paper in 2015, as indexed in the Web of Science (WoS). Psychology researchers were sampled to improve familiarity with the anchoring effect [@jacowitz1995;@tversky1974], for which summary results were fabricated. U.S. researchers were sampled to ensure familiarity with the imperial measurement system, which is the scale of some of the anchoring studies. WoS was searched on October 13, 2015. In total, 2,038 unique corresponding e-mails were extracted from 2,014 papers (due to multiple corresponding authors).

The full sample frame was digitally approached to participate in this study on April XX, 2016 (invitation: osf.io/s4w8r). The study took place via Qualtrics with anonimization procedures in place (e.g., no IP-address saved at all). The researchers were fully informed that the study would require them to fabricate data and that we conducted this study to test the validity of statistical methods to detect data fabrication. Participants were also informed they could stop at any time without providing a reason. If they wanted, participants received a $30 Amazon gift card as compensation for their participation for which they had to provide their email address. These email addresses were unlinked from email addresses upon completion of the study and sending out the gift cards.

@@

To detect data fabrication in a set of summary results, we first test the variance of fabricated standard deviations [SDs; @simonsohn2013] across the four anchoring studies. This method tests whether the observed SDs contain a reasonable amount of variation, as expected based on stochastic sampling processes. For example, if four independent samples all yield the variance of 2.22, this could be considered excessively consistent when the probability that this amount of consistency (or more), given genuine samples, is less than 1 out of 1000 (this is simply an example). To compute this test, we first standardize the SDs for each of the four studies by computing

$\tilde{s}_j=\frac{s^2_j}{MS_w}=\frac{s^2_j}{\frac{\sum(N_j-1)s^2_j}{\sum(N_j-1)}}$
<!--- \limits^k_{j=1} --->

where $\tilde{s}_j$ denotes the standardized SD in group *j*. Note that $MS_w$ is the simple arithmetic mean when sample sizes are equal for all cells. We test several different measures to detect data fabrication that utilize these standardized SDs (i.e., $\tilde{s}_j$), including the max-min distance (denoted $\tilde{\sigma}_{max-min}$) and the variance of the standardized SDs [i.e.,  $\tilde{\sigma}_{sd}$; @simonsohn2013]. We compare the observed value for each $\tilde{\sigma}$ measure with the expected distribution of outcomes when the data would be the result of random sampling processes. To this end, we simulate the expected distribution of standardized SDs and compute the expected distribution of each $\tilde{\sigma}$. This expected distribution is used to determine the *p*-value of the observed $\tilde{\sigma}$ value. We simulate the standardized SD for each of the *j* groups as

$\tilde{s}^2_j\sim\Bigg[\frac{\chi^2_{N_j-1}s^2_j}{N_j-1}\Bigg]/MS_w$

These simulated values are used to compute the expected distribution of all $\tilde{\sigma}$ measures.

Second, we apply the reversed Fisher method to the fabricated nonsignificant *p*-values twice, once for the gender effects hypothesis and once for the interaction effects hypothesis, in order to detect data fabrication. The Fisher method [@fisher1925] tests for evidence of an effect in a set of *p*-values and has previously been used as a meta-analytic method [@hong2008], but we adjust it here to test for results that are overly consistent with the null hypothesis. The original Fisher method is computed as

$\chi^2_{2k}=-2\sum\ln(p_i)$
<!--- \limits^k_{i=1} --->
